---
title: "video games"
author: "nehali"
date: "25/05/2020"
output: html_document
---
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tidyr)
```

```{r}
vgsales2019<- read.csv("data/sales-2019.csv")
vgsales2016 <- read.csv("data/sales-2016-with-ratings.csv")
```
```{r}
vgsales2016
```

```{r}
vgsales2019
```

```{r}
vgsales2016 %>%
  mutate(User_Score = as.numeric(User_Score))
vgsales2019 %>%
  mutate(User_Score = as.numeric(User_Score))
```


```{r}
summary(vgsales2016) 


```

```{r}
dim(vgsales2016)
head(vgsales2016)
```



```{r}
dim(vgsales2019)
head(vgsales2019)
```


```{r}
summary(vgsales2019)
```



```{r}
vgsales2019
```


```{r}
vg <- inner_join(vgsales2016, vgsales2019, by = c("Name"))
vg
```

```{r}
vg <- vg %>%
  mutate(
name = as.factor(vg$Name),
year = as.factor(vg$Year),

)
```
```{r}
vg1 <- vg %>%
  mutate(total_sales = NA_Sales.x + NA_Sales.y+ EU_Sales + JP_Sales.x + JP_Sales.y + Other_Sales.x + Other_Sales.y + Global_Sales.x +Global_Sales.y) %>%
mutate(total_NA_sales = NA_Sales.x + NA_Sales.y, total_JP_sales = JP_Sales.x + JP_Sales.y) 
vg1
```


```{r}
vg1 <- vg1 %>%
  arrange(desc(total_sales))
```

```{r}
dim(vg1)
```


```{r}
summary(vg1)
```
```{r}
str(vg1)
```

```{r}
rank = vg1$Rank
name = vg1$Name
platform = vg1$Platform
year = vg1$Year
genre = vg1$Genre
publisher = vg1$Publisher
NAsales = vg1$NA_Sales
EUsales = vg1$EU_Sales
JPsales = vg1$JP_Sales
otherSales = vg1$Other_Sales
globalSales = vg1$Global_Sales
Region = vg1$Region.where.most
```


```{r}
names(vg1)
```
x: 2016
y: 2019

```{r}
head(vg1, n = 10)
```
```{r}
tail(vg1, n= 10)
```



VISUALIZING YEARLY PRODUCTION

Yearly Production of video games

```{r}
library(ggthemes)
```



```{r}
plot(vg1$year, xlab = "year", ylab = "total_sales" , main = "Yearly Distribution of Video Games" ,col="red")
```

```{r}
vg1
```


Based on genre
```{r}
plot(vg1$Genre.x, xlab = "Genre", ylab = "total_sales", main="Genre Based Distribution-2016", col = "green")
```

```{r}
plot(vg1$Genre.y, xlab = "Genre", ylab = "total_sales", main="Genre Based Distribution-2019", col = "green")
```


Based on platform

2016
```{r}
  plot(vg1$Platform.x, xlab = "Platform", ylab = "No. of games", main="Platform
       Based Distribution", col = "green")
```
2019
```{r}
plot(vg1$Platform.y, xlab = "Platform", ylab = "No. of games", main="Platform Based Distribution", col = "green")
```

```{r}

library(ggplot2)
```
wrt Publisher-2016
```{r}
plot(vg1$Publisher.x, main = "Publisher based distribution 2016", xlab = "Publisher", ylab = "No. of games")
```
2019
```{r}
plot(vg1$Publisher.y, main = "Publisher based distribution 2019", xlab = "Publisher", ylab = "No. of games")
```

```{r}
vg1
```

Sales of games in NA wrt platform
```{r}
plot(vg1$Platform.x ~ vg1$NA_Sales.x, main = "Platform based distribution", xlab="", ylab = "No. of games with respect to platforms", col="cyan")
```




```{r}
vg1

```


```{r}
yearly_revenue <- vg1 %>%
filter(!is.na(total_sales)) %>%
  group_by(year) %>%
summarise(yearly_revenue = sum(total_sales))
yearly_revenue
```

```{r}
ggplot(yearly_revenue, aes(year, yearly_revenue)) +
  geom_bar(fill = "purple", stat = "identity") +
  ggtitle("Game Revenue by Year") +
  scale_x_discrete(name = "year", breaks = c(1980, 1990, 2000, 2010, 2020))
                       
```
```{r}
vg1
```
SALES BASED DISTRIBUTION


```{r}
library(ggplot2)
```
```{r}
vg1
```



```{r}
plot(vg1$Platform.y ~ vg1$Global_Sales.y, main = "Sales based distribution", ylab = "Games wrt platform", col = "pink")
```

TOP 30 PUBLISHERS for 2016


```{r}
top30_2016 <- vg1 %>%
  
filter(!is.na(Publisher.x)) %>%
  group_by(Publisher.x) %>%
count()
top30_2016

```
x: 2016
```{r}
top30_x <- top30_2016 %>%
  arrange(desc(n))
top30_x


```

```{r}
library(broom)
```




```{r}
plot(top30_x$Publisher.x, main = "Publisher based distribution 2016", xlab = "Publisher", ylab = "No. of games")
```


```{r}
top_10 <- top30_x %>%
  head(10)
top_10
```
 top 10 publishers of 2019
```{r}
top10_2019 <- vg1 %>%
  
filter(!is.na(Publisher.y)) %>%
  group_by(Publisher.y) %>%
count()
top10_2019
```

```{r}

cro(top_10$Publisher.x, top_10$n)
```






2019
```{r}
top30_y <- vg1 %>%
  
filter(!is.na(Publisher.y)) %>%
  group_by(Publisher.y) %>%
count()
top30_y
  
  
```

```{r}
top30_y <- top30_y%>%
  arrange(desc(n))
top30_y
```

```{r}
summary(top30_y)
```

vg1 = 2016 + 2019
.x = 2016
.y = 2019

```{r}
top30_y %>%
  filter(!is.na(Publisher.y))
```
```{r}
top30_x %>%
  filter(!is.na(Publisher.x))
```

```{r}
fj <- full_join(top30_x,top30_y) 
fj
```
```{r}
fj %>%
  arrange(desc(n))
```

```{r}
str(vg1)
```
```{r}
fj
```

```{r}
vg1
```





```{r}
library(ggiraphExtra)
library(GGally)
```




```{r}

mod1.x <- lm(NA_Sales.x ~ Genre.x, data = vg1)
mod1.x
summary(mod1.x)
```

intercept : 0.319917: 
p value < 0.05, hence there is no significant change in NA sales wrt genre.
R square is quite low, that means only 15 % of variation is explained by  Genre.
 
```{r}
mod1.y <- lm(NA_Sales.y ~ Genre.y, data = vg1)
mod1.y

```
```{r}
library(broom)
```

```{r}
tidy(mod1.x)
tidy(mod1.y)
```


```{r}
summary(mod1.y)
```
p value < 0.05, no significant change.
R square is 0.02532, which again is quite low but more then data for 2016.

```{r}
vg1
```


```{r}
mod2x<- lm(EUsales ~ Genre.x, data = vg1)
mod2x
```
```{r}
summary(mod2x)
```
p value < 0.05, reject .

```{r}
mod2y <- lm(EUsales ~ Genre.y, data = vg1)
mod2y
```

```{r}
summary(mod2y)
```

```{r}
vg1
```


```{r}
mod3.x <- lm(JP_Sales.x ~ Genre.x, data = vg1)
mod3.x
```
```{r}
summary(mod3.x)
```

```{r}
mod3.y <- lm(JP_Sales.y ~ Genre.y, data = vg1)
mod3.y
```
```{r}
summary(mod3.y)
```

for 2016
```{r}
library(car)
```

```{r}
scatterplotMatrix(formula = ~ NA_Sales.x + EU_Sales + JP_Sales.x , cex = 1, data=vg1, reg.line = ""  )
```

```{r}
autoplot(mod1.x)
autoplot(mod2x)
autoplot(mod3.x)
```
For mod1x: NAsales.x ~ genre.x : we can see that the relationship is linear.
Residuals are not noramlly distribute.
mod2x: EUsales ~ genre.x
mod3x: JPsales.x ~ genre.x

mod1y:NAsales.y ~ genre.y
mod2y:EU sales ~ genre.y
mod3y: JPsales.y ~ genre.y

  


for 2019

```{r}
scatterplotMatrix(formula = ~ NA_Sales.y + EU_Sales + JP_Sales.y , cex=1, data=vg1, reg.line=""  )
```

```{r}
library(ggfortify)
autoplot(mod1.y)
autoplot(mod2y)
autoplot(mod3.y)
```

mod1.y : Residual vs fitted : line is exactly on 0, linear pattern 









